The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-10 Manuscript/NBABubbleAnalysis.Rmd
hyperlinks for citations with asa bibstyle

---
title: "The Effects of the NBA COVID Bubble on the NBA Playoffs"
subtitle: "A Case Study for Home-Court Advantage"
author: |
  | Michael Price and Jun Yan
  | michael.price@uconn.edu
  | Department of Statistics, University of Connecticut
date: "`r format(Sys.time(), '%d, %B, %Y')`"
documentclass: article
papersize: letter
fontsize: 11pt
bibliography: citations.bib
biblio-style: asa
output: bookdown::pdf_document2
header-includes:
   - \usepackage[margin=1in]{geometry}
toc: False
---
Abstract: 
The 2020 NBA playoffs were played inside of a bubble in Disney World because of
the COVID-19 pandemic. This meant that there would be no fans in attendance, 
games played on neutral courts and no traveling for teams, which in theory 
removes home-court advantage from the games. This setting has attracted a lot of
discussion as analysts and fans debated the possible effects it may have on the
outcome of games. Home-court advantage has historically played a huge role in 
NBA playoff series outcomes. The 2020 playoff provided a unique
opportunituy to study the effects of the bubble, and home-court
advantage by comparing the 2020 season with the seasons in the past
While many factors contribute to the outcome of games, points scored
is the deciding factor of who wins games so scoring is the primary focus 
of this study. The specific measures of interest are team scoring totals and 
team shooting percentage on two pointers, three pointers, and free throws. 
Comparing these measures for home teams and away teams in 2020 vs. 2017-2019
shows that the 2020 playoffs favored away teams more than normal, particularly
with two point shooting and total scoring.

>>>>

---
title: "The Effects of the NBA COVID Bubble on the NBA Playoffs"
subtitle: "A Case Study for Home-Court Advantage"
author: |
  | Michael Price and Jun Yan
  | michael.price@uconn.edu
  | Department of Statistics, University of Connecticut
date: "`r format(Sys.time(), '%d, %B, %Y')`"
documentclass: article
papersize: letter
fontsize: 11pt
bibliography: citations.bib
biblio-style: asa
output: bookdown::pdf_document2
header-includes:
   - \usepackage[margin=1in]{geometry}
   - \usepackage {hyperref}
   - \hypersetup {colorlinks = true, linkcolor = blue, citecolor=blue, urlcolor = red}
toc: False
---
Abstract: 
The 2020 NBA playoffs were played inside of a bubble in Disney World because of
the COVID-19 pandemic. This meant that there would be no fans in attendance, 
games played on neutral courts and no traveling for teams, which in theory 
removes home-court advantage from the games. This setting has attracted a lot of
discussion as analysts and fans debated the possible effects it may have on the
outcome of games. Home-court advantage has historically played a huge role in 
NBA playoff series outcomes. The 2020 playoff provided a unique
opportunituy to study the effects of the bubble, and home-court
advantage by comparing the 2020 season with the seasons in the past
While many factors contribute to the outcome of games, points scored
is the deciding factor of who wins games so scoring is the primary focus 
of this study. The specific measures of interest are team scoring totals and 
team shooting percentage on two pointers, three pointers, and free throws. 
Comparing these measures for home teams and away teams in 2020 vs. 2017-2019
shows that the 2020 playoffs favored away teams more than normal, particularly
with two point shooting and total scoring.
